\huge A Usability Evaluation of Tor Launcher

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Fix BibTeX capitalization issue.
This is BibTeX, Version 0.99d (TeX Live 2016/Debian)
The top-level auxiliary file: pets2017-paper.aux
Case mismatch error between cite keys Xlab and xlab
---line 190 of file pets2017-paper.aux
 : \citation{Xlab
 :               }
I'm skipping whatever remains of this command

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{Xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.

>>>>

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.
